---
title: "Homework 0"
output: github_document
author: [Abzal Yessengazy]
---

### Task 1 - Implementation



I think I used too many if statements, but will do better next time. 

Secondly, I did not fullfill the condition within numeric inputs like 5.0 is acceptable and 5.1 is not. need to clarify during the workshop. 
All comments have # and are below. 


```{r}
fizzbuzz = function(vtr){ 
    for (v in vtr){ #using v to go through each element / number of vector vtr
        if (is.numeric(v) == TRUE) { #checks if the value is numeric i.e. double or integer
            if (v >= 0) { # checks if value is positive
                if (is.finite(v) == TRUE) { #checks if the value is finite
                    if (v %% 5 == 0 & v %% 3 == 0){print("Fizzbuzz")} #main fizzbuzz replacement code
                    else if (v %% 3 == 0) {print("Fizz")}
                    else if (v %% 5 == 0) {print("Buzz")}
                    else (print(v))   
                }
                else (print("ONLY finite Allowed")) #prints out errors and so on...
                            }
            else (print("ONLY Positive Allowed"))
        }
        else (print("ONLY Numeric Allowed"))
        
    }
       
}
```

### Task 2 - Validation & Testing

Below are a (incomplete) collection of test cases that have been separated into good and bad inputs. After you have implemented the function above check that the test cases below produce the correct output (or at least a useful error message).

#### Good Inputs

```{r}
fizzbuzz(1)
fizzbuzz(3)
fizzbuzz(5)
fizzbuzz(15)

fizzbuzz(9:15)
fizzbuzz(15:9)

fizzbuzz(1:12)
```


#### Bad Inputs

```{r error=TRUE}
fizzbuzz(-1)
fizzbuzz(-3)
fizzbuzz(-5)

fizzbuzz(TRUE)
fizzbuzz(FALSE)

fizzbuzz(Inf)
fizzbuzz(-Inf)
fizzbuzz(NaN)

fizzbuzz("A")
fizzbuzz(1.5)
fizzbuzz(1i)
fizzbuzz(4i)
```


